Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2025-02-25 paper.tex
Fix typo

\begin{equation}
  S_{g} = 1 - \frac{\sigma_L}{\sigma} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 - \varepsilon_L \cos{\psi}\right) \sqrt{1 - \varepsilon_L^2 \cos^2{\psi}}} \right|
  \label{eq:stationarity_g}
\end{equation}
Notice that the steady, linearised solutions depend on both the the wavenumber
ratio $k_L/k$ and the long-wave steepness $\varepsilon_L$.

>>>>

\begin{equation}
  S_{g} = 1 - \frac{\sigma_L}{\sigma} \left| \frac{\varepsilon_L \sin{\psi}}{\left(1 - \varepsilon_L \cos{\psi}\right) \sqrt{1 - \varepsilon_L^2 \cos^2{\psi}}} \right|
  \label{eq:stationarity_g}
\end{equation}
Notice that the steady, linearised solutions depend on both the wavenumber
ratio $k_L/k$ and the long-wave steepness $\varepsilon_L$.
